---
title: "CSE4027 - House Pricing"
output:
  html_notebook: default
  pdf_document: default
  word_document: default
---


# Linear Regression
This is a House Price Prediction Using Linear Regression  Model

At first we install all the required packages for the linear regression.
```{r}
install.packages('readr')
install.packages('ggplot2')
install.packages('mlbench')
install.packages('corrplot')
install.packages('Amelia')
install.packages('caret')
install.packages('plotly')
install.packages('caTools')
install.packages('reshape2')
install.packages('dplyr')
library(readr)
library(ggplot2)
library(corrplot)
library(mlbench)
library(Amelia)
library(plotly)
library(reshape2)
library(caret)
library(caTools)
library(dplyr)

```

We input the cleaned dataset
```{r}
data(Housing)
housing <- Housing
```

## Exploratory Data Analysis
### Visualizations

#### Correlation

```{r}
corrplot(cor(select(housing,-chas)))
```

#### Density Plot using ggplot2
```{r}
housing %>% 
  ggplot(aes(medv)) +
  stat_density() + 
  theme_bw()
```

#### Density Plot using plotly
```{r}
ggplotly(housing %>% 
  ggplot(aes(medv)) +
  stat_density() + 
  theme_bw())
```

#### medv
```{r}
housing %>%
  select(c(crim, rm, age, rad, tax, lstat, medv,indus,nox,ptratio,zn)) %>%
  melt(id.vars = "medv") %>%
  ggplot(aes(x = value, y = medv, colour = variable)) +
  geom_point(alpha = 0.7) +
  stat_smooth(aes(colour = "black")) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  labs(x = "Variable Value", y = "Median House Price ($1000s)") +
  theme_minimal()
```


## Model Building & Prediction
### Train and Test Data
```{r}
set.seed(123)
split <- sample.split(housing,SplitRatio =0.75)
train <- subset(housing,split==TRUE)
test <- subset(housing,split==FALSE)
```

### Training The Model
```{r}
model <- lm(medv ~ crim + rm + tax + lstat , data = train)
summary(model)
```
### Visualizing The Model
```{r}
res <- residuals(model)
res <- as.data.frame(res)
ggplot(res,aes(res)) +  geom_histogram(fill='blue',alpha=0.5)
```

```{r}
plot(model)
```


### Predictions
```{r}
test$predicted.medv <- predict(model,test)

pl1 <-test %>% 
  ggplot(aes(medv,predicted.medv)) +
  geom_point(alpha=0.5) + 
  stat_smooth(aes(colour='black')) +
  xlab('Actual value of medv') +
  ylab('Predicted value of medv')+
  theme_bw()

ggplotly(pl1)
```

### Assessing our Model
```{r}
error <- test$medv-test$predicted.medv
rmse <- sqrt(mean(error)^2)
```
